Modular Model-Checking of a Byzantine Fault-Tolerant Protocol

### 2017-02-27 paper/paper.tex
reviewers: added a little more intro text about state updates.

Let a transition system $\mathcal{M} = (S, I, \rightarrow)$, be a set of states $S$, a set of initial states $I \subseteq S$, and a transition relation $\rightarrow \subseteq S \times S$. We implicitly assume a set of state variables such that each $\sigma \in S$ is a total function that maps state variables to values. We distinguish two special state variables in a transition system: (1) $now \in \mathbb{R}$ denotes the current time in the state, and (2) $cal$ is an event calendar.

>>>>

Let a transition system $\mathcal{M} = (S, I, \rightarrow)$, be a set of states $S$, a set of initial states $I \subseteq S$, and a transition relation $\rightarrow \subseteq S \times S$. We implicitly assume a set of state variables such that each state $\sigma \in S$ is a total function that maps state variables to values. We sometimes prime a state to denote that satisfies the transition relation: $\sigma \rightarrow \sigma'$. We also sometimes use a variable assignment notation to describe what state variables are specifically updated: e.g., $\sigma' = \sigma[v := v+1]$.

We distinguish two special state variables in a transition system: (1) $now \in \mathbb{R}$ denotes the current time in the state, and (2) $cal$ is an event calendar.
